Optimizing Abstract Abstract Machines

### 2013-07-02 paper/paper.tex
Tightened some spacing to get into 12 pages.

Tracing the execution of the analysis reveals an immediate shortcoming: there is a high degree of branching and merging in the exploration.
%
Surveying this branching has no benefit for precision.
%
For example, in a function application, {\tt (f x y)}, where {\tt f}, {\tt x} and {\tt y} each have several values each argument evaluation induces $n$-way branching, only to be ultimately joined back together in their respective application positions.
%
Transition patterns of this shape litter the state-graph:
%
\begin{center}
\includegraphics[scale=0.2]{fanoutdot2}
\end{center}
To avoid the spurious forking and joining, we {\it delay} the non-determinism until and unless it is needed in {\it strict contexts} (such as the guard of an {\tt if}, a called procedure, or a numerical primitive application).
%
Doing so collapses these forks and joins into a linear sequence of states:
\begin{center}
\includegraphics[scale=0.2]{lazydot}
\end{center}
%%

@@

The store maps to a stack of timestamped sets of abstract values.
%
Throughout this section, we will be taking the parameter $t$ to be the ``current time,'' or the length of the store chain at the beginning of the step.

\begin{align*}
\msto \in \Store &= \Addr \to \Valstack \\
\mvalstack \in \Valstack &= (\Timestamp \times \wp(\Storeable))^*
\end{align*}

>>>>

Tracing the execution of the analysis reveals an immediate shortcoming: there is a high degree of branching and merging in the exploration.
%
Surveying this branching has no benefit for precision.
%
For example, in a function application, {\tt (f x y)}, where {\tt f}, {\tt x} and {\tt y} each have several values each argument evaluation induces $n$-way branching, only to be ultimately joined back together in their respective application positions.
%
Transition patterns of this shape litter the state-graph:
%
\vspace{-1em}
\begin{center}
\includegraphics[scale=0.2]{fanoutdot2}
\end{center}
\vspace{-1em}
To avoid the spurious forking and joining, we {\it delay} the non-determinism until and unless it is needed in {\it strict contexts} (such as the guard of an {\tt if}, a called procedure, or a numerical primitive application).
%
Doing so collapses these forks and joins into a linear sequence of states:
\vspace{-1em}
\begin{center}
\includegraphics[scale=0.2]{lazydot}
\end{center}
\vspace{-1em}
%%

@@

The store maps to a stack of timestamped sets of abstract values.
%
Throughout this section, we will be taking the parameter $t$ to be the ``current time,'' or the length of the store chain at the beginning of the step.
\vspace{-0.9em}
\begin{align*}
\msto \in \Store &= \Addr \to \Valstack \\
\mvalstack \in \Valstack &= (\Timestamp \times \wp(\Storeable))^*
\end{align*}
